### 2020-06-10 writeup/app_exp.tex
sec F

\textbf{Single-task based metric.}

@@

\textbf{Further results on covariance alignment.}
Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.

\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
		\caption{Task pair TREC and CR}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{Task pair MR and SST}
	\end{subfigure}
	\caption{The performance of aligning task covariances depends on data size. As the ratio between source task data size and target task data size increases, the performance improvement from aligning task covariances increases.}
	\label{fig_covariate_app}
\end{figure}

>>>>

\textbf{Single-task based metric.}
We simplify the setup of this experiment by fixing the sample sizes of every task pair.
For sentiment analysis tasks, the source task uses xx training samples and the target task uses xx training samples for every task pair.
For image classification tasks, the training sample size is 10,000 for every task.

@@

\iffalse
\textbf{Further results on covariance alignment.}
%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,

\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
		\caption{Task pair TREC and CR}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{Task pair MR and SST}
	\end{subfigure}
	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance. We suspect that this happens because of overfitting on the extra parameters in the additional covariance alignment module.}
	\label{fig_covariate_app}
\end{figure}
\fi
